What We Eval in the Shadows

### 2021-08-10 paper/main.tex
Update 5.1

The variety of uses of \eval is evidenced by the number of different forms. In
comparison, JavaScript \eval usage was more straightforward and more
predictable as reported by \citet{oopsla12b}, with 98.7\% of the sites with
only one form. On the other hand, there are \packageNbSimpleMinimizedOne sites
that only receive one of the simple forms (\ie\xspace \c{X}, \c{V}, \c{\$} or
\c{<-}). Additional \packageNbSimpleMinimizedMore sites takes multiple forms,
but all of them are these simple ones. Among these sites there are many cases
where \eval could be replaced by simpler constructs such as \c{get} to lookup a
name in an environment, \c{assign} to set a value to a name in an environment
or \c{do.call} to reflectively call a function.

>>>>

The number of different forms evidences the variety of uses of \eval. In
comparison, JavaScript \eval usage was more straightforward and more
predictable as reported by \citet{oopsla12b}, with 98.7\% of the sites with
only one form. On the other hand, there are \packageNbSimpleMinimizedOne sites
that only receive one of the simple forms (\ie\xspace \c{X}, \c{V}, \c{\$} or
\c{<-}). Additional \packageNbSimpleMinimizedMore sites take multiple forms,
but all of them are these simple ones. Among these sites, there are many cases
where \eval could be replaced by simpler constructs such as \c{get} to lookup a
name in an environment, \c{assign} to set a value to a name in an environment,
or \c{do.call} to call a function reflectively.
